Draft-assinment1

### 2017-02-15 Draft-xuezhou-sjb.Rmd
update

#Table of Contents
- 1.Introduction
* 2.Goal
* 3.Dataset Preparation
* 4.Objective
* 5.Summary of variables
 * 5.1 Individual variable summary
  * 5.1.1 School
   * 5.1.1.1 State
   * 5.1.1.2 Predominant Degree
   * 5.1.1.3 Control of Institution
  * 5.1.2 Student Body
    * 5.1.2.1 Percentage first-generation students
    * 5.1.2.2 Number of applications
  * 5.1.3 Cost 
    * 5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
    * 5.1.3.2 Percentage of students who are financially independent
  * 5.1.4 Financial Aid
    * 5.1.4.1 Percentage of undergraduates who receive a Pell Grant
    * 5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
    * 5.1.4.3 The median debt for students who have completed
    * 5.1.4.4 The median debt for students who have not completed
  * 5.1.5 Earning
    * 5.1.5.1 Median family income in real 2015 dollars
    * 5.1.5.2 Earning after graduation
  * 5.1.6 Repayment
    * 5.1.6.1 3-year Repayment rate
    * 5.1.6.2 3-year Default rate
* 6.Relationship between variables
 * 6.1 NPT4_COMBINE VS State
 * 6.2 Debt VS Cost
 * 6.3 Percentage of Pell Grant VS college type(CONTROL)
 * 6.4 Percentage first-generation students VS Statu
 * 6.5 family income with Pell Grant
 * 6.6 cost and median debts with earning
 * 6.7 default with earning
 * 6.8 degree type vs. earning
 * 6.9 predominant degree, control  and earning after 6 year of entry
 * 6.10 predominant degree + control (count)
 * 6.11 control + earning
* 7. Comparison between variables
* 8. Findings and Conclusion

>>>>

#Table of Contents
* 1.Introduction
* 2.Goal
* 3.Dataset Preparation
* 4.Objective
* 5.Summary of variables
 * 5.1 Individual variable summary
  * 5.1.1 School
   * 5.1.1.1 State
   * 5.1.1.2 Predominant Degree
   * 5.1.1.3 Control of Institution
  * 5.1.2 Student Body
    * 5.1.2.1 Percentage first-generation students
    * 5.1.2.2 Number of applications
  * 5.1.3 Cost 
    * 5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
    * 5.1.3.2 Percentage of students who are financially independent
  * 5.1.4 Financial Aid
    * 5.1.4.1 Percentage of undergraduates who receive a Pell Grant
    * 5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
    * 5.1.4.3 The median debt for students who have completed
    * 5.1.4.4 The median debt for students who have not completed
  * 5.1.5 Earning
    * 5.1.5.1 Median family income in real 2015 dollars
    * 5.1.5.2 Earning after graduation
  * 5.1.6 Repayment
    * 5.1.6.1 3-year Repayment rate
    * 5.1.6.2 3-year Default rate
* 6.Relationship between variables
 * 6.1 NPT4_COMBINE VS State
 * 6.2 Debt VS Cost
 * 6.3 Percentage of Pell Grant VS college type(CONTROL)
 * 6.4 Percentage first-generation students VS Statu
 * 6.5 family income with Pell Grant
 * 6.6 cost and median debts with earning
 * 6.7 default with earning
 * 6.8 degree type vs. earning
 * 6.9 predominant degree, control  and earning after 6 year of entry
 * 6.10 predominant degree + control (count)
 * 6.11 control + earning
* 7. Comparison between variables
* 8. Findings and Conclusion
